### 2023-03-17 chapter2/chapter2.tex
Added some sections to materials and methods of chapter 2

\section{Materials and methods}
Here's where my materials and methods will go!

>>>>

\section{Materials and methods}

\subsection{Alignment and tree generation}

\subsection{IDR prediction and filtering}

\subsection{Fitting substitution models}

\subsection{Brownian motion and Ornstein-Uhlenbeck analyses}

\subsection{Simulation analyses}

\subsection{Code and data availability}
The code used to produce the results and analyses is available at \url{https://github.com/marcsingleton/IDR_evolution2023}. The following Python libraries were used: matplotlib, NumPy, pandas, and SciPy~\cite{Hunter2007, Harris2020, McKinney2010, Virtanen2020}. Relevant output files are available in the supporting information. There is no primary data associated with this manuscript. All primary data are available from publicly accessible sources described in their corresponding sections.
